---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# SPRING

<!-- badges: start -->
<!-- badges: end -->

The R package `SPRING` (Semi-Parametric Rank-based approach for INference in Graphical model) estimate sparse microbial association networks using rank-based correlation with sparse graphical modeling techniques. The corresponding reference is

Yoon, Gaynanova and M&uuml;ller (2019) [Microbial Networks in SPRING - Semi-parametric Rank-Based Correlation and Partial Correlation Estimation for Quantitative Microbiome Data](https://www.frontiersin.org/articles/10.3389/fgene.2019.00516/full). *Frontiers in Genetics*, 10:516.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("GraceYoon/SPRING")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SPRING)
## basic example code
```

